\documentclass{article}
\usepackage[utf8]{inputenc}

%\usepackage{showframe}
\usepackage{tabularx}

% Math packages
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{stmaryrd}

\usepackage{enumitem}


\begin{document}

\title{Discussion}
\author{Paul Rousse}
\maketitle

\section{Nondeterminism in motion planning}
Show why it does not make sens to always take non determinism in account.

The controller is supposed to damp the effect of the noise, and the abstraction is supposed to hide all the unwanted effect of it.

Does it make sense to take the noise into account?
Can i find a situation where the noise needs to be taken in account?

Try to investiguate in the affine feedback, there might be a situation where we cannot damp the noise.
Maybe go for some computation of the affine feedback.


Advantages:
\begin{itemize}[noitemsep,topsep=0pt]
\item take the noise in account,
\item free some variable (but it is possible as well in Calin Belta method by changing the controller),
\item investigate the self loops/spurious loop suppression,
\item take in account the nondeterminism,
\item keep the timing information in the model,
\item maybe less assumption on the model,
\item not always possible to use fixed point technique, cannot handle any self loops, 
\item take in account the time drift problems that can occurs.
\end{itemize}

Inconvenients:
\begin{itemize}[noitemsep,topsep=0pt]
\item increase the complexity,
\item can be done with a deterministic model, where the lowlevel controller, take the noise in account,
\item need to consider just a fragment of LTL.
\end{itemize}

\end{document}
