\documentclass{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{nicefrac}
\usepackage{graphicx}
\usepackage{breqn}
\usepackage{tabularx}

\graphicspath{{./plots/}}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}
\newtheorem{problem}{Problem}

\newtheoremstyle{named}{}{}{\itshape}{}{\bfseries}{:\\}{.5em}{#1 \thmnote{(#3)}}
\theoremstyle{named}
\newtheorem*{namedtheorem}{Theorem}
\newtheorem*{nameddefinition}{Definition}

\usepackage[all]{xy}
\usepackage{amssymb}

\newdir{|>}{-{\scriptscriptstyle{\blacktriangleright}}}
\newcommand{\transition}{
  \ensuremath{ \xymatrix{\ar@{-|>}[r]&} }
  }
\newcommand{\labelledtransition}[1]{
  \ensuremath{ \xymatrix{\ar@{-|>}[r]^{#1}&} }
  }
  

\usepackage{cite}
 
\begin{document}


\title{Hierarchical control architecture}
\author{Paul Rousse}

\maketitle

\section{Introduction}

The model used in this master is compliant with a hierarchical control strategy: the model of the noise $\mathbf{w} \in \mathcal{W}$ is free (ie any perturbation will not create a direct feedback from the controller unlike piecewise affine feedback strategy).
This can be good benefit for complex task such as multiple-agent load lifting.
This come from the monotonic model.

The controller is not too constraining, other controllers can be modelled as noise on the model.

Most of the other approaches would have modelled this as markov chains, but here we can assert that if the controller is within the range $\mathcal{W}$, the LTL formula will be satisfied.

\textit{Try to think about an example that is simple, minimize the time, clean the room, sweep, load lifting algorithm damping swinging.}

\textit{Cite an article about hierarchical control, find right terms (inner/low level controller).}

I believe that there is a way of doing it with some other controllers, that it depends more on the low level controller that the quadricopter is using than on other  the fact that I am using the non determinism.

\cite{liu2014abstraction} really good intro for hierarchical control approaches.

\section{Swing damping}

We will just perform an experiment to show how such a hierarchical controller can work.



\bibliography{bibliography}{}
\bibliographystyle{plain}

\end{document}